%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Cover Letter - Luxoft, Data Analyst
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{cover}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{0pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     TITLE NAME
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{}{\Huge{Harsh Sachan}}{  \href{mailto:hsachan295@gmail.com}{hsachan295@gmail.com} | +91 8604304079 |  \urlstyle{same}\href{https://linkedin.com/in/harsh-sachan-b3b24a2a2}{LinkedIn} | \href{https://github.com/hsachan295-source}{GitHub}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     MAIN COVER LETTER CONTENT
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\currentdate{\today}
\lettercontent{Dear Hiring Team at Luxoft,}

\lettercontent{I am writing to express my strong interest in the Data Analyst position at Luxoft in Noida. As a final year B.Tech student in Computer Science Engineering with an AI Specialization from Galgotias College, and with a background in database modeling, SQL analytics, and BI dashboard engineering, I am excited to help Luxoft consolidate enterprise data and drive evidence-based operational recommendations.}

\lettercontent{Through my portfolio of independent projects, I have demonstrated the ability to own the complete data lifecycle—from ingestion and validation to reporting and optimization. Here is how my experience aligns with the core needs of this position:}

{\raggedright\fontspec[Path = OpenFonts/fonts/raleway/]{Raleway-Medium}\fontsize{11pt}{13pt}\selectfont
\begin{itemize}
    \item \textbf{Data Modeling \& Business Intelligence:} Designed a global AI/ML Jobs Market Analytics Power BI dashboard, architecting star-schema models and writing custom DAX measures to analyze salaries, remote work demand, and hiring trends.
    \item \textbf{Data Quality \& Validation:} Engineered NexCart, a FastAPI backend with Pydantic v2 cross-field schema validation, establishing strict rules for product inventory metrics.
    \item \textbf{Telemetry \& Data Consolidation:} Built AuraWeather, integrating REST API data ingestion with caching for automated daily condition-based reporting, containerized with Docker.
\end{itemize}\par}
\vspace{6pt}

\lettercontent{Luxoft's mission to improve the reliability, quality, and observability of IT services through analytical rigour matches my focus on building structured databases. My SQL scripting credentials (HackerRank SQL Advanced) and Oracle Certified OCI Data Science background make me highly equipped to contribute to your data governance and service delivery teams.}

\lettercontent{I bring a self-motivated, proactive approach to upskilling and problem-solving, and I thrive in collaborative engineering environments. I look forward to the opportunity to discuss how my technical skills can drive value for Luxoft.}

\lettercontent{Thank you for your time and consideration.}

\begin{flushright}
\closing{Sincerely,}

\signature{Harsh Sachan}
\end{flushright}
\end{document}
