%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Cover Letter - Cubist, ML Engineer
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{cover}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{0pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}
\begin{document}

\namesection{}{\Huge{Harsh Sachan}}{  \href{mailto:hsachan295@gmail.com}{hsachan295@gmail.com} | +91 8604304079 |  \urlstyle{same}\href{https://linkedin.com/in/harsh-sachan-b3b24a2a2}{LinkedIn} | \href{https://github.com/hsachan295-source}{GitHub}
}

\currentdate{\today}
\lettercontent{Dear Hiring Team at Cubist Systematic Strategies,}

\lettercontent{I am writing to express my strong interest in the Machine Learning Engineer, GenAI Technology position at Cubist Systematic Strategies in Bengaluru. As a final year CSE (AI Specialization) student from Galgotias College and an Oracle Certified OCI Data Science Professional, I have focused my development work on building Retrieval-Augmented Generation (RAG) agents, vector databases, and semantic search pipelines. I am excited to apply my hands-on GenAI experience to support Cubist's systematic research.}

\lettercontent{I focus on creating robust, high-performance AI solutions. I have built several projects that demonstrate my ability to own the complete Generative AI lifecycle:}

{\raggedright\fontspec[Path = OpenFonts/fonts/raleway/]{Raleway-Medium}\fontsize{11pt}{13pt}\selectfont
\begin{itemize}
    \item \textbf{Agentic RAG \& Vector Databases:} Built a semantic search and question-answering pipeline using Pinecone vector database, implementing agentic knowledge retrieval using LangChain and the Gemini API.
    \item \textbf{Sequence Modeling \& NLP:} Developed NeuralClass, a GRU-based sequence classifier served via FastAPI and containerized with Docker, establishing custom diagnostics logging.
    \item \textbf{Structured Data Architectures:} Engineered NexCart, a FastAPI and Streamlit system, utilizing Pydantic v2 cross-field validators to manage catalog constraints and schemas.
\end{itemize}\par}
\vspace{6pt}

\lettercontent{Cubist's focus on translating cutting-edge AI research into robust, high-performance systematic strategies aligns with my focus on building clean, validated python code, managing vector indexes (Pinecone/ChromaDB), and deploying containerized models. I am highly motivated to relocate to Bengaluru and collaborate with your quantitative researchers.}

\lettercontent{I bring a strong self-starter mindset and a passion for engineering robust LLM architectures. I look forward to the opportunity to discuss how my GenAI and database projects can add value to Cubist.}

\lettercontent{Thank you for your time and consideration.}

\begin{flushright}
\closing{Sincerely,}

\signature{Harsh Sachan}
\end{flushright}
\end{document}
