%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Cover Letter - Sun King, ML Engineer
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{cover}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{0pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}
\begin{document}

\namesection{}{\Huge{Harsh Sachan}}{  \href{mailto:hsachan295@gmail.com}{hsachan295@gmail.com} | +91 8604304079 |  \urlstyle{same}\href{https://linkedin.com/in/harsh-sachan-b3b24a2a2}{LinkedIn} | \href{https://github.com/hsachan295-source}{GitHub}
}

\currentdate{\today}
\lettercontent{Dear Hiring Team at Sun King,}

\lettercontent{I am writing to express my strong interest in the Machine Learning Engineer position at Sun King. As a final year B.Tech student in Computer Science Engineering (AI Specialization) from Galgotias College and an Oracle Certified OCI Data Science Professional, I have focused my development work on building deep learning models, computer vision systems, and deploying scalable REST endpoints. I am excited to apply my hands-on experience to help Sun King design and deploy production-grade models.}

\lettercontent{I focus on creating deployable, production-ready AI features. I have built several projects that demonstrate my ability to own the complete deep learning lifecycle:}

{\raggedright\fontspec[Path = OpenFonts/fonts/raleway/]{Raleway-Medium}\fontsize{11pt}{13pt}\selectfont
\begin{itemize}
    \item \textbf{Computer Vision \& Deep Learning:} Developed SavorShield, a CNN-based image classification model for fruit freshness detection using TensorFlow/Keras, implementing custom image preprocessing and data augmentation.
    \item \textbf{Cloud Deployment \& MLOps:} Containerized multiple deep learning pipelines (including NeuralPrice ANN and NeuralClass GRU models) using Docker and deployed them to Hugging Face Spaces for real-time public inference.
    \item \textbf{Low-Latency API Design:} Served models via FastAPI and Flask REST APIs, establishing strict data schemas and diagnostics reporting.
\end{itemize}\par}
\vspace{6pt}

\lettercontent{Sun King's focus on building production-grade deep learning models for speech/audio and computer vision use cases matches my experience in utilizing TensorFlow, Keras, and OpenCV. I am highly suited for a remote role in India and eager to collaborate with your software and product teams.}

\lettercontent{I bring a strong self-starter mindset and a passion for engineering robust deep learning systems. I look forward to discussing how my computer vision and cloud deployment projects can contribute to Sun King's AI features.}

\lettercontent{Thank you for your time and consideration.}

\begin{flushright}
\closing{Sincerely,}

\signature{Harsh Sachan}
\end{flushright}
\end{document}
