%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Cover Letter - Cloudflare, ML Engineer
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{cover}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{0pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}
\begin{document}

\namesection{}{\Huge{Harsh Sachan}}{  \href{mailto:hsachan295@gmail.com}{hsachan295@gmail.com} | +91 8604304079 |  \urlstyle{same}\href{https://linkedin.com/in/harsh-sachan-b3b24a2a2}{LinkedIn} | \href{https://github.com/hsachan295-source}{GitHub}
}

\currentdate{\today}
\lettercontent{Dear Hiring Team at Cloudflare,}

\lettercontent{I am writing to express my interest in the Machine Learning Engineer position at Cloudflare. As a final year B.Tech student in Computer Science Engineering (AI Specialization) from Galgotias College and an Oracle Certified OCI Data Science Professional, I have focused my development projects on model reproducibility, REST API optimization, and containerized deployments. I am excited to apply my hands-on experience to help Cloudflare scale its ML systems.}

\lettercontent{I believe that performance, scalability, and security are critical for deployment. I have built several projects highlighting my deployment and pipeline optimization skills:}

{\raggedright\fontspec[Path = OpenFonts/fonts/raleway/]{Raleway-Medium}\fontsize{11pt}{13pt}\selectfont
\begin{itemize}
    \item \textbf{Data Pipeline Ingestion \& Caching:} Built AuraWeather, containerizing the Streamlit dashboard with Docker and implementing query caching on REST API ingestion to minimize latency and data overhead.
    \item \textbf{API Design \& Validation:} Engineered NexCart, a FastAPI product management system with Pydantic v2 cross-field validators to ensure data quality and telemetry logging.
    \item \textbf{Docker Containerization:} Packaged several deep learning pipelines (including NeuralPrice ANN and NeuralClass GRU models) into Docker containers and deployed them to Hugging Face Spaces for real-time serving.
\end{itemize}\par}
\vspace{6pt}

\lettercontent{Cloudflare's dedication to scaling web services globally matches my commitment to data validation, REST API performance, and Docker containerization. I am eager to join your engineering teams and work on high-speed, scalable ML solutions.}

\lettercontent{I bring a proactive learning mindset and a passion for data pipeline optimization. I look forward to discussing how my containerization and API deployment projects can add value to Cloudflare.}

\lettercontent{Thank you for your time and consideration.}

\begin{flushright}
\closing{Sincerely,}

\signature{Harsh Sachan}
\end{flushright}
\end{document}
