%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Cover Letter - Jumio, ML Engineer
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{cover}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{0pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}
\begin{document}

\namesection{}{\Huge{Harsh Sachan}}{  \href{mailto:hsachan295@gmail.com}{hsachan295@gmail.com} | +91 8604304079 |  \urlstyle{same}\href{https://linkedin.com/in/harsh-sachan-b3b24a2a2}{LinkedIn} | \href{https://github.com/hsachan295-source}{GitHub}
}

\currentdate{\today}
\lettercontent{Dear Hiring Team at Jumio,}

\lettercontent{I am writing to express my interest in the Machine Learning Engineer position at Jumio. As a final year B.Tech student in Computer Science Engineering specializing in AI from Galgotias College and an Oracle Certified OCI Data Science Professional, I have focused my development work on building deep learning models, computer vision classifiers, and deploying secure REST endpoints. I am excited to apply my hands-on experience to support Jumio's ID verification and fraud detection solutions.}

\lettercontent{I focus on creating reliable, secure deep learning solutions. I have built several projects that demonstrate my ability to own the complete modeling lifecycle:}

{\raggedright\fontspec[Path = OpenFonts/fonts/raleway/]{Raleway-Medium}\fontsize{11pt}{13pt}\selectfont
\begin{itemize}
    \item \textbf{Computer Vision \& Modeling:} Developed SavorShield, a CNN-based image classification model for fruit freshness detection using TensorFlow/Keras, implementing custom image preprocessing and data augmentation.
    \item \textbf{Secure API Deployments:} Served deep learning models via FastAPI and Flask REST APIs, establishing strict schema validation (using Pydantic) and custom prediction logging.
    \item \textbf{Containerization \& Cloud:} Containerized multiple deep learning pipelines (including NeuralPrice ANN and NeuralClass GRU models) using Docker and deployed them to Hugging Face Spaces for real-time inference.
\end{itemize}\par}
\vspace{6pt}

\lettercontent{Jumio's mission to develop state-of-the-art fraud detection and ID verification matches my focus on building robust, validated data models and containerized deployments. I am highly motivated to join your engineering teams and work with your advanced computer vision algorithms.}

\lettercontent{I bring a strong self-starter mindset and a passion for engineering secure, robust models. I look forward to the opportunity to discuss how my computer vision and cloud deployment projects can add value to Jumio.}

\lettercontent{Thank you for your time and consideration.}

\begin{flushright}
\closing{Sincerely,}

\signature{Harsh Sachan}
\end{flushright}
\end{document}
