%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Cover Letter - Adobe, ML Engineer 2
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{cover}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{0pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}
\begin{document}

\namesection{}{\Huge{Harsh Sachan}}{  \href{mailto:hsachan295@gmail.com}{hsachan295@gmail.com} | +91 8604304079 |  \urlstyle{same}\href{https://linkedin.com/in/harsh-sachan-b3b24a2a2}{LinkedIn} | \href{https://github.com/hsachan295-source}{GitHub}
}

\currentdate{\today}
\lettercontent{Dear Hiring Team at Adobe,}

\lettercontent{I am writing to express my strong interest in the Machine Learning Engineer 2 position at Adobe in Bangalore. As a graduating Computer Science Engineering (AI Specialization) student from Galgotias College and an Oracle Certified OCI Data Science Professional, I have spent my academic career mastering the end-to-end ML lifecycle. I am excited to apply my hands-on experience in building and deploying deep learning models to support Adobe's creative suite.}

\lettercontent{I focus on creating deployable, production-ready AI solutions. I have built several projects that demonstrate my ability to own the complete machine learning workflow:}

{\raggedright\fontspec[Path = OpenFonts/fonts/raleway/]{Raleway-Medium}\fontsize{11pt}{13pt}\selectfont
\begin{itemize}
    \item \textbf{Model Engineering \& Preprocessing:} Trained a 4-layer Artificial Neural Network (ANN) using TensorFlow, preprocessing 337 custom features via one-hot encoding, and delivering real-time predictions across multiple currencies.
    \item \textbf{Full ML Lifecycle Deployment:} Containerized multiple models using Docker and deployed them to Hugging Face Spaces (such as my GRU-based NLP classifier and CNN fruit freshness model).
    \item \textbf{API Development:} Developed secure, high-performance REST APIs in FastAPI and Flask to serve deep learning models with live diagnostics and prediction logging.
\end{itemize}\par}
\vspace{6pt}

\lettercontent{Adobe's focus on high-quality software architectures and feature development aligns with my methodical approach to model validation, schema enforcement (using Pydantic), and reproducible container configurations. I am eager to collaborate with your engineering teams to translate complex AI research into customer-facing products.}

\lettercontent{I bring a strong problem-solving mindset and a passion for continuous technical upskilling. I look forward to the opportunity to discuss how my ML engineering background can contribute to the Adobe Illustrator and creative engineering teams.}

\lettercontent{Thank you for your time and consideration.}

\begin{flushright}
\closing{Sincerely,}

\signature{Harsh Sachan}
\end{flushright}
\end{document}
