%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Cover Letter - Qualys, MLOps Engineer
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{cover}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{0pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}
\begin{document}

\namesection{}{\Huge{Harsh Sachan}}{  \href{mailto:hsachan295@gmail.com}{hsachan295@gmail.com} | +91 8604304079 |  \urlstyle{same}\href{https://linkedin.com/in/harsh-sachan-b3b24a2a2}{LinkedIn} | \href{https://github.com/hsachan295-source}{GitHub}
}

\currentdate{\today}
\lettercontent{Dear Hiring Team at Qualys,}

\lettercontent{I am writing to express my interest in the Machine Learning Operations Engineer position at Qualys. As a final year B.Tech student in Computer Science Engineering specializing in AI from Galgotias College, and an Oracle Certified OCI Data Science Professional, I have focused my development projects on model reproducibility, containerization, and API deployments. I am excited to apply my hands-on MLOps experiences to support Qualys' enterprise security systems.}

\lettercontent{I believe that training models is only half the battle; ensuring reproducible and scalable deployment is key. I have built several systems highlighting my deployment skills:}

{\raggedright\fontspec[Path = OpenFonts/fonts/raleway/]{Raleway-Medium}\fontsize{11pt}{13pt}\selectfont
\begin{itemize}
    \item \textbf{Docker Containerization:} Packaged several machine learning pipelines (including NeuralPrice ANN and NeuralClass GRU models) into Docker containers to ensure clean, environment-independent execution.
    \item \textbf{Cloud Deployment \& MLOps:} Deployed containerized applications to Hugging Face Spaces, setting up REST API endpoints to serve public real-time inference.
    \item \textbf{Pipeline Automation \& Caching:} Built AuraWeather, containerizing the Streamlit dashboard with Docker and implementing query caching on API ingestion to prevent pipeline bottlenecks.
\end{itemize}\par}
\vspace{6pt}

\lettercontent{Qualys' mission to transform enterprise systems through AI matches my commitment to data governance, schema validation (using FastAPI/Pydantic), and version control (Git/GitHub). I am highly motivated to work with your security and MLOps engineering teams in Pune.}

\lettercontent{I bring a proactive, self-directed upskilling mindset and a passion for engineering robust systems. I look forward to discussing how my containerization and pipeline deployment projects can add value to Qualys' MLOps workflows.}

\lettercontent{Thank you for your time and consideration.}

\begin{flushright}
\closing{Sincerely,}

\signature{Harsh Sachan}
\end{flushright}
\end{document}
