%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Cover Letter - Nielsen, ML Engineer
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{cover}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{0pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}
\begin{document}

\namesection{}{\Huge{Harsh Sachan}}{  \href{mailto:hsachan295@gmail.com}{hsachan295@gmail.com} | +91 8604304079 |  \urlstyle{same}\href{https://linkedin.com/in/harsh-sachan-b3b24a2a2}{LinkedIn} | \href{https://github.com/hsachan295-source}{GitHub}
}

\currentdate{\today}
\lettercontent{Dear Hiring Team at Nielsen,}

\lettercontent{I am writing to express my strong interest in the Machine Learning Engineer position at Nielsen in Bengaluru. As a final year B.Tech student in Computer Science Engineering specializing in AI from Galgotias College and an Oracle Certified OCI Data Science Professional, I have focused my development work on building deep learning models, structured data schemas, and custom analytics dashboards. I am excited to apply my machine learning experience to support Nielsen's analytics systems.}

\lettercontent{I focus on creating reliable, data-driven systems. I have designed and deployed several projects that demonstrate my ability to own the complete modeling lifecycle:}

{\raggedright\fontspec[Path = OpenFonts/fonts/raleway/]{Raleway-Medium}\fontsize{11pt}{13pt}\selectfont
\begin{itemize}
    \item \textbf{Marketplace Insights \& Data Modeling:} Designed an executive-level Power BI dashboard analyzing global hiring trends, salaries, and remote work, architecting star-schema models and writing custom DAX measures.
    \item \textbf{Deep Learning \& Predictive Modeling:} Trained a 4-layer Artificial Neural Network (ANN) using TensorFlow, preprocessing 337 features, containerized with Docker, and deployed on Hugging Face.
    \item \textbf{Data Pipeline Engineering:} Built AuraWeather, integrating API telemetry ingestion with custom query caching to reduce latency.
\end{itemize}\par}
\vspace{6pt}

\lettercontent{Nielsen's focus on building and deploying robust, scalable ML pipelines aligns with my experience in database optimization (SQL), REST API design (FastAPI/Flask), and Docker containerization. I am highly motivated to relocate to Bengaluru and collaborate with your teams to translate data into functional ML solutions.}

\lettercontent{I bring a proactive, self-starter approach and a passion for engineering robust models. I look forward to the opportunity to discuss how my technical skills can add value to Nielsen.}

\lettercontent{Thank you for your time and consideration.}

\begin{flushright}
\closing{Sincerely,}

\signature{Harsh Sachan}
\end{flushright}
\end{document}
