%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Cover Letter - GoDaddy, ML Scientist
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{cover}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{0pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}
\begin{document}

\namesection{}{\Huge{Harsh Sachan}}{  \href{mailto:hsachan295@gmail.com}{hsachan295@gmail.com} | +91 8604304079 |  \urlstyle{same}\href{https://linkedin.com/in/harsh-sachan-b3b24a2a2}{LinkedIn} | \href{https://github.com/hsachan295-source}{GitHub}
}

\currentdate{\today}
\lettercontent{Dear Hiring Team at GoDaddy,}

\lettercontent{I am writing to express my strong interest in the Machine Learning Scientist position at GoDaddy in Gurugram. As a graduating Computer Science Engineering student specializing in AI from Galgotias College, and an Oracle Certified OCI Data Science Professional, I have focused my projects on building intelligent web systems and search architectures. I am excited to apply my data modeling, API engineering, and GenAI experience to simplify and improve the shopping journey for GoDaddy's entrepreneurs.}

\lettercontent{I believe that Machine Learning should drive direct user value. I have built several projects targeting E-commerce modeling, catalog management, and semantic indexing that align with GoDaddy's objectives:}

{\raggedright\fontspec[Path = OpenFonts/fonts/raleway/]{Raleway-Medium}\fontsize{11pt}{13pt}\selectfont
\begin{itemize}
    \item \textbf{E-Commerce Product Engineering:} Built NexCart, a FastAPI and Streamlit system with Pydantic v2 cross-field validators to manage product listings, pricing, and volume conversions with interactive KPI analytics.
    \item \textbf{Semantic Search \& Retrieval:} Designed an Agentic RAG System utilizing LangChain and Pinecone vector store to perform similarity search and context-aware PDF question answering.
    \item \textbf{Marketplace Insights:} Engineered a global AI/ML Jobs Market dashboard in Power BI, using star-schema models and advanced DAX measures to analyze salary distributions and remote job trends.
\end{itemize}\par}
\vspace{6pt}

\lettercontent{GoDaddy's focus on building a cohesive navigation experience across channels matches my experience in integrating databases and developing APIs for downstream services. Living in Gurugram's commuting distance (Greater Noida), I am ready to collaborate hybridly and support your core ML teams in training and scaling models.}

\lettercontent{I bring a proactive, research-driven mindset to engineering new solutions. I look forward to the opportunity to discuss how my ML modeling and E-commerce dashboard projects can contribute to GoDaddy's navigation and search experiences.}

\lettercontent{Thank you for your time and consideration.}

\begin{flushright}
\closing{Sincerely,}

\signature{Harsh Sachan}
\end{flushright}
\end{document}
