%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Cover Letter - JioStar, ML Engineer I
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{cover}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{0pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}
\begin{document}

\namesection{}{\Huge{Harsh Sachan}}{  \href{mailto:hsachan295@gmail.com}{hsachan295@gmail.com} | +91 8604304079 |  \urlstyle{same}\href{https://linkedin.com/in/harsh-sachan-b3b24a2a2}{LinkedIn} | \href{https://github.com/hsachan295-source}{GitHub}
}

\currentdate{\today}
\lettercontent{Dear Hiring Team at JioStar,}

\lettercontent{I am writing to express my strong interest in the Machine Learning Engineer I position at JioStar in Bengaluru. As a final year B.Tech student in Computer Science Engineering (AI Specialization) from Galgotias College and an Oracle Certified OCI Data Science Professional, I have focused my development work on building NLP pipelines, text classifiers, and agentic search architectures. I am excited to apply my hands-on experience to help JioStar design scalable AI features.}

\lettercontent{I have engineered several NLP and search systems that demonstrate my ability to own the complete model development lifecycle:}

{\raggedright\fontspec[Path = OpenFonts/fonts/raleway/]{Raleway-Medium}\fontsize{11pt}{13pt}\selectfont
\begin{itemize}
    \item \textbf{Sequence Modeling \& NLP:} Built NeuralClass, a GRU-based text sequence model for classification, served via FastAPI, containerized with Docker, and deployed on Hugging Face Spaces.
    \item \textbf{Semantic Search \& RAG:} Designed an Agentic RAG System utilizing LangChain and Pinecone vector store, integrating the Gemini API to resolve queries over unstructured document archives.
    \item \textbf{Full-Stack API Design:} Engineered NexCart, a FastAPI and Streamlit system, utilizing Pydantic v2 cross-field validators to manage database constraints and inventory telemetry.
\end{itemize}\par}
\vspace{6pt}

\lettercontent{JioStar's focus on building high-attention media experiences matches my experience in integrating models with low-latency REST APIs and optimizing inference runtimes. I am highly motivated to relocate to Bengaluru and collaborate with your engineering teams to develop production-grade AI solutions.}

\lettercontent{I bring a proactive learning mindset and a strong foundation in machine learning. I look forward to the opportunity to discuss how my development skills can contribute to JioStar's ML engineering projects.}

\lettercontent{Thank you for your time and consideration.}

\begin{flushright}
\closing{Sincerely,}

\signature{Harsh Sachan}
\end{flushright}
\end{document}
