%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Cover Letter - Expedia, ML Engineer II
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{cover}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{0pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}
\begin{document}

\namesection{}{\Huge{Harsh Sachan}}{  \href{mailto:hsachan295@gmail.com}{hsachan295@gmail.com} | +91 8604304079 |  \urlstyle{same}\href{https://linkedin.com/in/harsh-sachan-b3b24a2a2}{LinkedIn} | \href{https://github.com/hsachan295-source}{GitHub}
}

\currentdate{\today}
\lettercontent{Dear Hiring Team at Expedia Group,}

\lettercontent{I am writing to express my interest in the Machine Learning Engineer II (Data Engineering Heavy) position at Expedia Group in Gurgaon. As a final year B.Tech student in Computer Science Engineering (AI Specialization) from Galgotias College, and an advanced SQL specialist certified by HackerRank, I have built several projects focused on data validation, REST APIs, and database modeling. I am excited to apply my data engineering skills to support Expedia's marketplace analytics.}

\lettercontent{I focus on creating reliable, automated data pipelines. I have designed projects that showcase my ability to handle complex databases and schemas:}

{\raggedright\fontspec[Path = OpenFonts/fonts/raleway/]{Raleway-Medium}\fontsize{11pt}{13pt}\selectfont
\begin{itemize}
    \item \textbf{Data Schema \& API Validation:} Engineered NexCart, a FastAPI REST system with Pydantic v2 cross-field validators to automate business schema calculations and ensure data quality in transactional catalogs.
    \item \textbf{Data Pipeline Ingestion:} Built AuraWeather, a Streamlit dashboard that ingests weather API payloads, implements query caching to reduce load, and processes hourly coordinates data.
    \item \textbf{Data Modeling:} Architected a global hiring trends analytics database in Power BI using star-schema principles and custom DAX measures for executive reporting.
\end{itemize}\par}
\vspace{6pt}

\lettercontent{Expedia's emphasis on scaling production ML pipelines and managing transactional data aligns with my focus on database optimization (PostgreSQL/MySQL) and Docker containerization. Living in Greater Noida, I am highly suited for the Gurgaon work location and eager to join your engineering teams.}

\lettercontent{I bring a strong problem-solving mindset and a passion for data pipeline reliability. I look forward to discussing how my database engineering skills can add value to Expedia's travel platforms.}

\lettercontent{Thank you for your time and consideration.}

\begin{flushright}
\closing{Sincerely,}

\signature{Harsh Sachan}
\end{flushright}
\end{document}
