%% Tailored CV for Adobe - ML Engineer 2
%% Compiled with: lualatex main_adobe.tex

\documentclass[11pt,a4paper,sans]{moderncv}
\moderncvstyle{banking}
\moderncvcolor{blue}

\renewcommand*{\firstnamestyle}[1]{{\fontsize{34}{36}\bfseries\upshape\color{color1}#1}}
\renewcommand*{\lastnamestyle}[1]{{\fontsize{34}{36}\bfseries\upshape\color{color1}#1}}
\renewcommand*{\sectionstyle}[1]{{\sectionfont\color{color1}#1}}

\usepackage[utf8]{inputenc}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,
    urlcolor=blue,
    pdftitle={Harsh Sachan - Adobe ML Engineer 2 CV},
    pdfpagemode=FullScreen,
}
\usepackage[scale=0.80]{geometry}
\usepackage{import}

\name{Harsh}{Sachan}
\address{Greater Noida, Uttar Pradesh, India}{}{}
\phone[mobile]{+91 8604304079}
\email{hsachan295@gmail.com}
\extrainfo{\href{https://linkedin.com/in/harsh-sachan-b3b24a2a2}{LinkedIn} | \href{https://github.com/hsachan295-source}{GitHub} | \href{https://leetcode.com/Harshsachan2001/}{LeetCode}}

\begin{document}

\makecvtitle

\vspace{6pt}
\small{Aspiring Machine Learning Engineer with a B.Tech in CSE (AI Specialization) from Galgotias College. Strong expertise in the full machine learning lifecycle from exploratory data analysis (EDA) and feature engineering to neural network modeling, API serving (FastAPI/Flask), Docker containerization, and Hugging Face deployment. Certified OCI Data Science Professional with hands-on experience building robust predictive models, computer vision systems, and NLP pipelines.}

\section{Core Competencies}
\vspace{1pt}
\begin{itemize}
\item \textbf{Machine Learning \& Deep Learning}: TensorFlow, Keras, Scikit-Learn, ANN, CNN, GRU, LSTM, Supervised \& Unsupervised Learning, Regression, Classification
\item \textbf{Frontend \& Backend}: React.js, Tailwind CSS, Node.js, Express.js, JWT Authentication, HTML5, CSS3
\item \textbf{Languages \& Databases}: Python, SQL, C++, Java, PostgreSQL, MySQL, MongoDB, Pinecone, ChromaDB
\item \textbf{Cloud \& Deployment}: Docker, Hugging Face Spaces, Git, GitHub, OCI, GCP
\end{itemize}

\section{Projects \& Experience}
\vspace{3pt}
\begin{itemize}

\item{\cventry{2024}{NeuralPrice -- AI Laptop Price Predictor}{Independent}{Greater Noida, India}{}{\vspace{1pt}
\begin{itemize}
    \item Engineered a 4-layer ANN with 337 features using TensorFlow and Scikit-Learn for real-time laptop price prediction.
    \item Owned the complete ML lifecycle: from EDA and feature engineering to training, evaluation, and serving.
    \item Containerized with Docker and deployed on Hugging Face Spaces for real-time model inference.
\end{itemize}}}

\vspace{3pt}

\item{\cventry{2024}{NeuralClass -- NLP Spam Classifier}{Independent}{Greater Noida, India}{}{\vspace{1pt}
\begin{itemize}
    \item Trained a GRU-based sequence model for text classification, served via FastAPI, containerized with Docker, and deployed on Hugging Face Spaces.
\end{itemize}}}

\vspace{3pt}

\item{\cventry{2025}{SavorShield -- Fruit Freshness Classifier}{Independent}{Greater Noida, India}{}{\vspace{1pt}
\begin{itemize}
    \item Developed a CNN-based image classification model for fruit freshness detection using TensorFlow/Keras and Flask.
    \item Deployed a Flask inference pipeline on Hugging Face Spaces demonstrating out-of-distribution model generalization.
\end{itemize}}}

\end{itemize}

\section{Education}
\vspace{1pt}
\begin{itemize}
\item{\cventry{2022--2026}{B.Tech in Computer Science Engineering (AI Specialization)}{Galgotias College of Engineering and Technology}{Greater Noida, UP, India}{}{\vspace{1pt}
CGPA: 8.12 / 10.0\\
Key Courses: Machine Learning, Deep Learning, Natural Language Processing, Computer Vision, Generative AI.
}}
\end{itemize}

\section{Languages}
\vspace{1pt}
\begin{itemize}
\item English (Professional), Hindi (Native).
\end{itemize}

\section{Certifications}
\vspace{1pt}
\begin{itemize}
\item \textbf{Oracle}: OCI 2025 Certified Data Science Professional | OCI 2025 Certified AI Foundations Associate
\item \textbf{IBM}: IBM SkillsBuild: Introduction to Artificial Intelligence
\item \textbf{HackerRank}: SQL (Advanced), Problem Solving, Software Engineer Intern
\end{itemize}

\section{References}
\vspace{1pt}
\begin{itemize}
\item Available upon request.
\end{itemize}

\end{document}
