%% Tailored CV for Roku - ML Engineer
%% Compiled with: lualatex main_roku.tex

\documentclass[11pt,a4paper,sans]{moderncv}
\moderncvstyle{banking}
\moderncvcolor{blue}

\renewcommand*{\firstnamestyle}[1]{{\fontsize{34}{36}\bfseries\upshape\color{color1}#1}}
\renewcommand*{\lastnamestyle}[1]{{\fontsize{34}{36}\bfseries\upshape\color{color1}#1}}
\renewcommand*{\sectionstyle}[1]{{\sectionfont\color{color1}#1}}

\usepackage[utf8]{inputenc}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,
    urlcolor=blue,
    pdftitle={Harsh Sachan - Roku ML Engineer CV},
    pdfpagemode=FullScreen,
}
\usepackage[scale=0.80]{geometry}
\usepackage{import}

\name{Harsh}{Sachan}
\address{Greater Noida, Uttar Pradesh, India}{}{}
\phone[mobile]{+91 8604304079}
\email{hsachan295@gmail.com}
\extrainfo{\href{https://linkedin.com/in/harsh-sachan-b3b24a2a2}{LinkedIn} | \href{https://github.com/hsachan295-source}{GitHub} | \href{https://leetcode.com/Harshsachan2001/}{LeetCode}}

\begin{document}

\makecvtitle

\vspace{6pt}
\small{Aspiring Machine Learning Engineer with a B.Tech in CSE (AI Specialization) from Galgotias College. Strong foundation in deep learning models (ANN, CNN, GRU), text sequence modeling, and RAG pipelines. Skilled in SQL querying, Python scripting, and MLOps deployment (Docker, Hugging Face, cloud APIs).}

\section{Core Competencies}
\vspace{1pt}
\begin{itemize}
\item \textbf{Machine Learning \& Deep Learning}: TensorFlow, Keras, Scikit-Learn, ANN, CNN, GRU, LSTM, Supervised/Unsupervised Learning, Regression, Classification
\item \textbf{Languages \& Databases}: Python, SQL, C++, Java, PostgreSQL, MySQL, MongoDB, Pinecone, ChromaDB
\item \textbf{Data Pipelines \& APIs}: FastAPI, Flask, Streamlit, Pandas, NumPy, Matplotlib, Plotly, REST Ingestion
\item \textbf{GenAI \& Tools}: RAG, LangChain, Pinecone, Docker, Hugging Face, Git, GitHub
\end{itemize}

\section{Projects \& Experience}
\vspace{3pt}
\begin{itemize}

\item{\cventry{2024}{NeuralPrice -- AI Laptop Price Predictor}{Independent}{Greater Noida, India}{}{\vspace{1pt}
\begin{itemize}
    \item Engineered a 4-layer ANN with 337 features via one-hot encoding; containerized with Docker and deployed on Hugging Face.
    \item Preprocessed custom datasets to achieve low prediction error across multiple currencies.
\end{itemize}}}

\vspace{3pt}

\item{\cventry{2024}{NeuralClass -- NLP Spam Classifier}{Independent}{Greater Noida, India}{}{\vspace{1pt}
\begin{itemize}
    \item Built a GRU-based sequence model for classification, served via FastAPI, containerized with Docker, and deployed on Hugging Face.
\end{itemize}}}

\vspace{3pt}

\item{\cventry{2025}{AuraWeather -- Real-Time Weather Analytics Dashboard}{Independent}{Greater Noida, India}{}{\vspace{1pt}
\begin{itemize}
    \item Weather analytics dashboard with geocoding, Plotly visualizations, and data ingestion caching.
\end{itemize}}}

\end{itemize}

\section{Education}
\vspace{1pt}
\begin{itemize}
\item{\cventry{2022--2026}{B.Tech in Computer Science Engineering (AI Specialization)}{Galgotias College of Engineering and Technology}{Greater Noida, UP, India}{}{\vspace{1pt}
CGPA: 8.12 / 10.0\\
Key Topics: Deep Learning, Natural Language Processing, Computer Vision, Databases, Machine Learning.
}}
\end{itemize}

\section{Languages}
\vspace{1pt}
\begin{itemize}
\item English (Professional), Hindi (Native).
\end{itemize}

\section{Certifications}
\vspace{1pt}
\begin{itemize}
\item \textbf{Oracle}: OCI 2025 Certified Data Science Professional | OCI 2025 Certified AI Foundations Associate
\item \textbf{HackerRank}: SQL (Advanced), Problem Solving, Software Engineer Intern
\item \textbf{Experiences}: Google Cloud GenAI | TATA, Deloitte, Walmart Virtual Experience Certifications
\end{itemize}

\section{References}
\vspace{1pt}
\begin{itemize}
\item Available upon request.
\end{itemize}

\end{document}
