%% Tailored CV for GoDaddy - ML Scientist
%% Compiled with: lualatex main_godaddy.tex

\documentclass[11pt,a4paper,sans]{moderncv}
\moderncvstyle{banking}
\moderncvcolor{blue}

\renewcommand*{\firstnamestyle}[1]{{\fontsize{34}{36}\bfseries\upshape\color{color1}#1}}
\renewcommand*{\lastnamestyle}[1]{{\fontsize{34}{36}\bfseries\upshape\color{color1}#1}}
\renewcommand*{\sectionstyle}[1]{{\sectionfont\color{color1}#1}}

\usepackage[utf8]{inputenc}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,
    urlcolor=blue,
    pdftitle={Harsh Sachan - GoDaddy ML Scientist CV},
    pdfpagemode=FullScreen,
}
\usepackage[scale=0.80]{geometry}
\usepackage{import}

\name{Harsh}{Sachan}
\address{Greater Noida, Uttar Pradesh, India}{}{}
\phone[mobile]{+91 8604304079}
\email{hsachan295@gmail.com}
\extrainfo{\href{https://linkedin.com/in/harsh-sachan-b3b24a2a2}{LinkedIn} | \href{https://github.com/hsachan295-source}{GitHub} | \href{https://leetcode.com/Harshsachan2001/}{LeetCode}}

\begin{document}

\makecvtitle

\vspace{6pt}
\small{Aspiring Machine Learning Scientist and Data Scientist specializing in AI systems, E-commerce data architectures, and GenAI workflows. Experienced in building Retrieval-Augmented Generation (RAG) agents, custom search pipelines, and full-stack web products. Proven ability to architect star-schema data models and train neural networks, combining software engineering with advanced statistical and machine learning methodologies.}

\section{Core Competencies}
\vspace{1pt}
\begin{itemize}
\item \textbf{Generative AI \& Agents}: RAG pipelines, Agentic AI, ReAct Agents, Tool Calling, LangGraph Workflows, Prompt Engineering, Semantic Search, Embeddings
\item \textbf{Data Science \& ML}: Python, SQL, Scikit-Learn, TensorFlow, Keras, Supervised/Unsupervised Learning, Power BI dashboard design, Star Schemas, DAX, AB Testing concepts
\item \textbf{Languages \& Databases}: Python, SQL, C++, Java, PostgreSQL, MySQL, MongoDB, Pinecone, ChromaDB
\item \textbf{Frontend \& Backend}: React.js, Tailwind CSS, Node.js, Express.js, JWT Authentication, FastAPI, Streamlit
\end{itemize}

\section{Projects \& Experience}
\vspace{3pt}
\begin{itemize}

\item{\cventry{2025}{Team Task Manager}{Independent}{Greater Noida, India}{}{\vspace{1pt}
\begin{itemize}
    \item Full Stack MERN application for project \& task management with role-based access control, JWT authentication.
    \item Designed and built a dynamic glassmorphism dashboard styled with Tailwind CSS.
\end{itemize}}}

\vspace{3pt}

\item{\cventry{2025}{CineSuggest -- Premium AI Movie Recommendation System}{Independent}{Greater Noida, India}{}{\vspace{1pt}
\begin{itemize}
    \item Flask content-based filtering system (TF-IDF vectorizer + Cosine Similarity matching 39k+ films in under 0.05s).
    \item Features Autocomplete, backdrop blurring, and HTML5 Canvas poster generation.
\end{itemize}}}

\vspace{3pt}

\item{\cventry{2025}{Agentic RAG System with Gemini and Pinecone}{Independent}{Greater Noida, India}{}{\vspace{1pt}
\begin{itemize}
    \item Developed a Retrieval-Augmented Generation system using Gemini and Pinecone for semantic vector storage and similarity search.
\end{itemize}}}

\end{itemize}

\section{Education}
\vspace{1pt}
\begin{itemize}
\item{\cventry{2022--2026}{B.Tech in Computer Science Engineering (AI Specialization)}{Galgotias College of Engineering and Technology}{Greater Noida, UP, India}{}{\vspace{1pt}
CGPA: 8.12 / 10.0\\
Key Topics: Machine Learning, Deep Learning, Generative AI \& Agents, Vector Databases, SQL.
}}
\end{itemize}

\section{Languages}
\vspace{1pt}
\begin{itemize}
\item English (Professional), Hindi (Native).
\end{itemize}

\section{Certifications}
\vspace{1pt}
\begin{itemize}
\item \textbf{Oracle}: OCI 2025 Certified Data Science Professional | OCI 2025 Certified AI Foundations Associate
\item \textbf{IBM}: IBM SkillsBuild: Introduction to Artificial Intelligence
\item \textbf{HackerRank}: SQL (Advanced), Problem Solving, Software Engineer Intern
\end{itemize}

\section{References}
\vspace{1pt}
\begin{itemize}
\item Available upon request.
\end{itemize}

\end{document}
