\documentclass[a4paper,9pt]{article}

\usepackage[left=0.38in,right=0.38in,top=0.28in,bottom=0.28in]{geometry}
\usepackage[hidelinks]{hyperref}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}

\pagestyle{empty}

\titleformat{\section}{\normalsize\bfseries\uppercase}{}{0em}{}[\titlerule]
\titlespacing*{\section}{0pt}{5pt}{3pt}

\setlist[itemize]{leftmargin=1.3em,itemsep=0pt,topsep=1pt,parsep=0pt}

\newcommand{\resumeItem}[1]{\item\small #1}

\begin{document}

\begin{center}
{\Large \textbf{HARSH SACHAN}}\\[2pt]
{\small Data Analyst $|$ Data Scientist $|$ Machine Learning Engineer $|$ AI Engineer}\\[2pt]
{\small
+91-8604304079 ~$|$~
\href{mailto:hsachan295@gmail.com}{hsachan295@gmail.com} ~$|$~
\href{https://github.com/hsachan295-source}{github.com/hsachan295-source} ~$|$~
\href{https://www.linkedin.com/in/harsh-sachan-b3b24a2a2}{linkedin.com/in/harsh-sachan}
}
\end{center}

\vspace{-3mm}

\section{Education}
\noindent
\textbf{Galgotias College of Engineering and Technology}, Greater Noida, UP \hfill Aug 2022 -- Jun 2026\\
\textit{Bachelor of Technology in Computer Science Engineering (AI Specialization)} \hfill CGPA: 8.12/10.0

\vspace{-2mm}

\section{Technical Skills}
\noindent
\begin{tabular}{@{}p{2.3cm} p{15.1cm}}
\textbf{Languages:}   & Python, SQL, C++, Java \\[1pt]
\textbf{Data \& BI:}  & Microsoft Excel, Power Query, Power BI, DAX, Pivot Tables, Slicers, Conditional Formatting, Data Cleaning, ETL \\[1pt]
\textbf{Databases:}   & MySQL, PostgreSQL, MongoDB, Pinecone (Vector DB), Astra DB, Database Design, Views, Stored Procedures, CTEs \\[1pt]
\textbf{ML / DL:}     & Regression, Classification, Clustering, Decision Trees, Random Forest, XGBoost, ANN, CNN, RNN, GRU \\[1pt]
\textbf{Frameworks:}  & Scikit-Learn, TensorFlow, Keras, LangChain, LangGraph, FastAPI, Flask, Streamlit \\[1pt]
\textbf{GenAI \& Agents:}& RAG, Agentic AI, ReAct Agents, Tool Calling, OpenAI API, Gemini API, Prompt Engineering, Embeddings \\[1pt]
\textbf{Tools/Cloud:} & Git, GitHub, Docker, Hugging Face, Google Cloud, Oracle Cloud Infrastructure \\
\end{tabular}

\vspace{-2mm}

\section{Projects}

\noindent\textbf{IPL Performance Dashboard} $|$ \textit{Microsoft Excel, Power Query, Pivot Tables, Slicers, Data Analysis} \hfill
\href{https://github.com/hsachan295-source/Power-BI-Portfolio}{\small GitHub}
\begin{itemize}
\resumeItem{Built an interactive IPL performance dashboard using Pivot Tables, Pivot Charts, Slicers, and dynamic Excel charting.}
\resumeItem{Analyzed team, player, and match metrics (runs, wickets, strike rate, win margins) across multi-year datasets.}
\resumeItem{Leveraged Power Query for automated data cleaning, merging, and structural transformations of raw IPL datasets.}
\end{itemize}

\vspace{1pt}
\noindent\textbf{HR Attrition Analysis Dashboard} $|$ \textit{Microsoft Excel, Pivot Tables, Charts, Slicers, HR Analytics} \hfill
\href{https://github.com/hsachan295-source/Power-BI-Portfolio}{\small GitHub}
\begin{itemize}
\resumeItem{Developed an interactive HR analytics dashboard to monitor and analyze employee attrition trends.}
\resumeItem{Visualized attrition metrics dynamically by department, age group, gender, salary brackets, and specific job roles.}
\resumeItem{Utilized conditional formatting and advanced Excel charts to surface actionable workforce retention insights.}
\end{itemize}

\vspace{1pt}
\noindent\textbf{SQL Data Analysis Project} $|$ \textit{SQL, MySQL, Window Functions, CTEs, Database Optimization} \hfill
\href{https://github.com/hsachan295-source/smart-business-dashboard}{\small GitHub}
\begin{itemize}
\resumeItem{Performed comprehensive data analysis and business reporting on transactional databases using advanced MySQL queries.}
\resumeItem{Implemented complex JOINs, GROUP BY/HAVING statements, Subqueries, Stored Procedures, and Database Views.}
\resumeItem{Optimized query performance by structured schema modeling and leveraging Common Table Expressions (CTEs) and Window Functions.}
\end{itemize}

\vspace{1pt}
\noindent\textbf{AI \& ML Jobs Market Analytics Dashboard} $|$ \textit{Power BI, DAX, Star Schema, Data Modeling} \hfill
\href{https://github.com/hsachan295-source/Power-BI-Portfolio}{\small GitHub}
\begin{itemize}
\resumeItem{Designed and published a Power BI dashboard analyzing global hiring trends, salaries, and remote job distributions in AI/ML.}
\resumeItem{Engineered a robust Star Schema model, mapping active/inactive relationships and optimization cross-filter propagation.}
\resumeItem{Wrote advanced calculated measures and time-intelligence metrics using DAX to drive dynamic data visualizations.}
\end{itemize}

\vspace{1pt}
\noindent\textbf{NeuralPrice -- AI Laptop Price Predictor} $|$ \textit{ANN, TensorFlow, Docker, Hugging Face} \hfill
\href{https://huggingface.co/spaces/Harsh0809/laptop-price-predictor-Ann}{\small Live} $|$
\href{https://github.com/hsachan295-source/Laptop-Price-Prediction-ANN}{\small GitHub}
\begin{itemize}
\resumeItem{Engineered a 4-layer Artificial Neural Network (ANN) with 337 engineered features using TensorFlow for price prediction.}
\resumeItem{Built end-to-end pipeline with StandardScaler preprocessing, one-hot encoding, Docker containerization, and Hugging Face deployment.}
\end{itemize}

\vspace{1pt}
\noindent\textbf{Agentic RAG with Gemini and Pinecone} $|$ \textit{RAG, Pinecone, LangChain, Gemini} \hfill
\href{https://github.com/hsachan295-source/Agentic-RAG-with-Gemini-and-Pinecone}{\small GitHub}
\begin{itemize}
\resumeItem{Developed a Retrieval-Augmented Generation system using Gemini and Pinecone for semantic vector storage and similarity search.}
\resumeItem{Built agentic workflows for PDF context retrieval and question-answering with automated search tools.}
\end{itemize}

\vspace{-2mm}

\section{Certifications}
\begin{itemize}
\resumeItem{\textbf{Oracle:} OCI 2025 Certified Data Science Professional ~$|$~ OCI 2025 Certified AI Foundations Associate}
\resumeItem{\textbf{HackerRank:} SQL (Advanced), Problem Solving, Software Engineer Intern ~$|$~ \textbf{Google Cloud:} Introduction to Generative AI}
\resumeItem{\textbf{Virtual Experience:} TATA GenAI Data Analytics ~$|$~ Deloitte Data Analytics ~$|$~ Walmart Advanced Software Engineering}
\end{itemize}

\vspace{-2mm}

\section{Achievements}
\begin{itemize}
\resumeItem{Built and deployed \textbf{12+ data analytics and AI/ML applications} featuring SQL databases, BI dashboards, and model deployment.}
\resumeItem{End-to-end lifecycle expertise: database modeling, query optimization, advanced dashboarding (Excel/Power BI), and ML predictive models.}
\resumeItem{Strong problem-solving foundation: HackerRank Advanced SQL certified, with expertise in data structures and query design.}
\end{itemize}

\end{document}
