%% Tailored CV for Qualys - MLOps Engineer
%% Compiled with: lualatex main_qualys.tex

\documentclass[11pt,a4paper,sans]{moderncv}
\moderncvstyle{banking}
\moderncvcolor{blue}

\renewcommand*{\firstnamestyle}[1]{{\fontsize{34}{36}\bfseries\upshape\color{color1}#1}}
\renewcommand*{\lastnamestyle}[1]{{\fontsize{34}{36}\bfseries\upshape\color{color1}#1}}
\renewcommand*{\sectionstyle}[1]{{\sectionfont\color{color1}#1}}

\usepackage[utf8]{inputenc}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,
    urlcolor=blue,
    pdftitle={Harsh Sachan - Qualys MLOps Engineer CV},
    pdfpagemode=FullScreen,
}
\usepackage[scale=0.80]{geometry}
\usepackage{import}

\name{Harsh}{Sachan}
\address{Greater Noida, Uttar Pradesh, India}{}{}
\phone[mobile]{+91 8604304079}
\email{hsachan295@gmail.com}
\extrainfo{\href{https://linkedin.com/in/harsh-sachan-b3b24a2a2}{LinkedIn} | \href{https://github.com/hsachan295-source}{GitHub} | \href{https://leetcode.com/Harshsachan2001/}{LeetCode}}

\begin{document}

\makecvtitle

\vspace{6pt}
\small{Aspiring MLOps Engineer with a B.Tech in CSE (AI Specialization) from Galgotias College. Strong hands-on experience in containerizing applications with Docker, deploying models on Hugging Face Spaces, and building REST APIs (FastAPI/Flask). Oracle Certified OCI Data Science Professional with a deep understanding of pipeline reproducibility, version control, and data validation.}

\section{Core Competencies}
\vspace{1pt}
\begin{itemize}
\item \textbf{MLOps \& Infrastructure}: Docker Containerization, API Deployment, Hugging Face Spaces, Git, GitHub, Version Control, Continuous Integration concepts, Oracle Cloud Infrastructure (OCI), GCP
\item \textbf{Data Pipelines \& APIs}: FastAPI, Flask, Streamlit, PostgreSQL, MySQL, MongoDB, Pinecone, Data Ingestion, Query Caching
\item \textbf{Machine Learning \& Deep Learning}: TensorFlow, Keras, Scikit-Learn, ANN, CNN, GRU, LSTM, Model Validation
\item \textbf{Data Libraries}: Pandas, NumPy, Matplotlib, Seaborn, Plotly, Power BI, Star Schema
\end{itemize}

\section{Projects \& Experience}
\vspace{3pt}
\begin{itemize}

% --- Project 1 ---
\item{\cventry{2024}{NeuralPrice -- AI Laptop Price Predictor}{Independent}{Greater Noida, India}{}{\vspace{1pt}
\begin{itemize}
    \item Preprocessed and trained a 4-layer ANN model using TensorFlow and Scikit-Learn.
    \item Containerized the complete Python ML pipeline with Docker for reproducible environments.
    \item Deployed the container on Hugging Face Spaces to serve public real-time inference.
\end{itemize}}}

\vspace{3pt}

% --- Project 2 ---
\item{\cventry{2024}{NeuralClass -- NLP Spam Classifier}{Independent}{Greater Noida, India}{}{\vspace{1pt}
\begin{itemize}
    \item Built and served a GRU sequence classifier via a FastAPI REST API with custom prediction logging.
    \item Containerized with Docker and deployed on Hugging Face Spaces for cloud serving.
\end{itemize}}}

\vspace{3pt}

% --- Project 3 ---
\item{\cventry{2025}{AuraWeather -- Real-Time Weather Analytics Dashboard}{Independent}{Greater Noida, India}{}{\vspace{1pt}
\begin{itemize}
    \item Designed weather telemetry dashboard, containerized using Docker for reproducible deployment.
    \item Integrated REST API ingestion with local caching to optimize pipeline performance.
\end{itemize}}}

\end{itemize}

\section{Education}
\vspace{1pt}
\begin{itemize}
\item{\cventry{2022--2026}{B.Tech in Computer Science Engineering (AI Specialization)}{Galgotias College of Engineering and Technology}{Greater Noida, UP, India}{}{\vspace{1pt}
CGPA: 8.12 / 10.0\\
Key Topics: Software Engineering, Database Systems, Machine Learning, Deep Learning, MLOps concepts.
}}
\end{itemize}

\section{Languages}
\vspace{1pt}
\begin{itemize}
\item English (Professional), Hindi (Native).
\end{itemize}

\section{Certifications}
\vspace{1pt}
\begin{itemize}
\item \textbf{Oracle}: OCI 2025 Certified Data Science Professional | OCI 2025 Certified AI Foundations Associate
\item \textbf{HackerRank}: SQL (Advanced), Problem Solving, Software Engineer Intern
\item \textbf{Experiences}: Google Cloud GenAI | TATA, Deloitte, Walmart Virtual Experience Certifications
\end{itemize}

\section{References}
\vspace{1pt}
\begin{itemize}
\item Available upon request.
\end{itemize}

\end{document}
