\documentclass[a4paper,9pt]{article}

\usepackage[left=0.38in,right=0.38in,top=0.28in,bottom=0.28in]{geometry}
\usepackage[hidelinks]{hyperref}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}

\pagestyle{empty}

\titleformat{\section}{\normalsize\bfseries\uppercase}{}{0em}{}[\titlerule]
\titlespacing*{\section}{0pt}{5pt}{3pt}

\setlist[itemize]{leftmargin=1.3em,itemsep=0pt,topsep=1pt,parsep=0pt}

\newcommand{\resumeItem}[1]{\item\small #1}

\begin{document}

\begin{center}
{\Large \textbf{HARSH SACHAN}}\\[2pt]
{\small Data Scientist $|$ Machine Learning Engineer $|$ AI Engineer $|$ Data Analyst}\\[2pt]
{\small
+91-8604304079 ~$|$~
\href{mailto:hsachan295@gmail.com}{hsachan295@gmail.com} ~$|$~
\href{https://github.com/hsachan295-source}{github.com/hsachan295-source} ~$|$~
\href{https://www.linkedin.com/in/harsh-sachan-b3b24a2a2}{linkedin.com/in/harsh-sachan}
}
\end{center}

\vspace{-3mm}

\section{Education}
\noindent
\textbf{Galgotias College of Engineering and Technology}, Greater Noida, UP \hfill Aug 2022 -- Jun 2026\\
\textit{Bachelor of Technology in Computer Science Engineering (AI Specialization)} \hfill CGPA: 8.12/10.0

\vspace{-2mm}

\section{Technical Skills}
\noindent
\begin{tabular}{@{}p{2.3cm} p{15.1cm}}
\textbf{Languages:}   & Python, SQL, C++, Java \\[1pt]
\textbf{ML / DL:}     & Regression, Classification, Clustering, Decision Trees, Random Forest, XGBoost, ANN, CNN, RNN, LSTM, GRU \\[1pt]
\textbf{Frameworks:}  & TensorFlow, Keras, Scikit-Learn, LangChain, LangGraph, FastAPI, Flask, Streamlit \\[1pt]
\textbf{Data \& BI:}  & Pandas, NumPy, Matplotlib, Seaborn, Power BI, Excel, DAX \\[1pt]
\textbf{Databases:}   & PostgreSQL, MySQL, MongoDB, Pinecone (Vector DB), Astra DB \\[1pt]
\textbf{Tools/Cloud:} & Git, GitHub, Docker, Hugging Face, Google Cloud, Oracle Cloud Infrastructure \\[1pt]
\textbf{GenAI:}       & OpenAI API, Gemini API, Mistral AI, Prompt Engineering, Embeddings, Semantic Search \\[1pt]
\textbf{AI/Agents:}   & RAG, Agentic AI, ReAct Agents, Tool Calling, LangGraph Workflows, Tavily Search, Ollama \\
\end{tabular}

\vspace{-2mm}

\section{Projects}

\noindent\textbf{Ollama Code Assistant} $|$ \textit{Python, Gradio, Ollama, CodeLlama, Modelfile} \hfill
\href{https://github.com/hsachan295-source/Ollama-Code-Assistant}{\small GitHub}
\begin{itemize}
\resumeItem{Developed an interactive, local AI Code Teaching Assistant named "AmitCodes" built with Python and Gradio.}
\resumeItem{Customized a local CodeLlama model via custom Modelfile settings (system prompt persona, temperature) for beginner-friendly programming support.}
\end{itemize}

\vspace{1pt}
\noindent\textbf{Astra DB PDF RAG with Ollama} $|$ \textit{Astra DB, Ollama, LangChain, PyPDF2, RAG} \hfill
\href{https://github.com/hsachan295-source/astra-db-pdf-rag-ollama}{\small GitHub}
\begin{itemize}
\resumeItem{Developed a Retrieval-Augmented Generation (RAG) system using Astra DB for cloud vector database storage.}
\resumeItem{Integrated Ollama locally for generating vector embeddings (nomic-embed-text) and chat response generation (gemma3:1b) using LangChain.}
\end{itemize}

\vspace{1pt}
\noindent\textbf{NeuralPrice -- AI Laptop Price Predictor} $|$ \textit{ANN, TensorFlow, Docker, Hugging Face} \hfill
\href{https://huggingface.co/spaces/Harsh0809/laptop-price-predictor-Ann}{\small Live} $|$
\href{https://github.com/hsachan295-source/Laptop-Price-Prediction-ANN}{\small GitHub}
\begin{itemize}
\resumeItem{Engineered a 4-layer ANN with 337 engineered features using TensorFlow and Scikit-Learn for real-time laptop price prediction.}
\resumeItem{Built end-to-end pipeline with StandardScaler preprocessing, one-hot encoding, Docker containerization, and Hugging Face deployment.}
\end{itemize}

\vspace{1pt}
\noindent\textbf{NeuralClass -- NLP Text Classifier} $|$ \textit{GRU, TensorFlow, FastAPI, Docker} \hfill
\href{https://huggingface.co/spaces/Harsh0809/gru-text-classifier}{\small Live} $|$
\href{https://github.com/hsachan295-source/Email-Spam-Detector}{\small GitHub}
\begin{itemize}
\resumeItem{Built a GRU-based spam/ham classification model using TensorFlow/Keras with confidence scoring and prediction logging.}
\resumeItem{Developed FastAPI inference APIs with Docker containerization and Hugging Face Spaces deployment.}
\end{itemize}

\vspace{1pt}
\noindent\textbf{SavorShield -- Fruit Freshness Classifier} $|$ \textit{CNN, TensorFlow, Flask} \hfill
\href{https://huggingface.co/spaces/Harsh0809/fruit-quality-classification-cnn}{\small Live} $|$
\href{https://github.com/hsachan295-source/Fruit-Quality-Classification-CNN}{\small GitHub}
\begin{itemize}
\resumeItem{Developed a CNN-based image classification model for Fresh vs Rotten fruit detection using TensorFlow/Keras and Flask.}
\end{itemize}

\vspace{1pt}
\noindent\textbf{AI-Powered Discord Assistant} $|$ \textit{LangChain, LangGraph, Gemini, Tavily, ReAct} \hfill
\href{https://github.com/hsachan295-source/AI-Powered-Discord-Assistant}{\small GitHub}
\begin{itemize}
\resumeItem{Built an intelligent Discord chatbot with ReAct-based agent workflows, real-time Tavily web search, and Google Gemini LLM.}
\end{itemize}

\vspace{1pt}
\noindent\textbf{Agentic RAG with Gemini and Pinecone} $|$ \textit{RAG, Pinecone, LangChain, Gemini} \hfill
\href{https://github.com/hsachan295-source/Agentic-RAG-with-Gemini-and-Pinecone}{\small GitHub}
\begin{itemize}
\resumeItem{Developed a Retrieval-Augmented Generation system using Gemini and Pinecone for semantic vector storage and similarity search.}
\end{itemize}

\vspace{1pt}
\noindent\textbf{AI \& ML Jobs Market Analytics Dashboard} $|$ \textit{Power BI, DAX, Star Schema}
\begin{itemize}
\resumeItem{Designed a Power BI dashboard analyzing AI/ML hiring trends, salary distributions, and remote job demand across global markets.}
\end{itemize}

\vspace{-2mm}

\section{Certifications}
\begin{itemize}
\resumeItem{\textbf{Oracle:} OCI 2025 Certified Data Science Professional ~$|$~ OCI 2025 Certified AI Foundations Associate}
\resumeItem{\textbf{HackerRank:} SQL (Advanced), Problem Solving, Software Engineer Intern ~$|$~ \textbf{Google Cloud:} Introduction to Generative AI}
\resumeItem{\textbf{Virtual Experience:} TATA GenAI Data Analytics ~$|$~ Deloitte Data Analytics ~$|$~ Walmart Advanced Software Engineering}
\end{itemize}

\vspace{-2mm}

\section{Achievements}
\begin{itemize}
\resumeItem{Built and deployed \textbf{12+ AI/ML and Generative AI applications} including NLP, Computer Vision, RAG systems, and Agentic workflows.}
\resumeItem{End-to-end ML lifecycle expertise: data preprocessing, feature engineering, model training, API development, and cloud deployment.}
\resumeItem{Strong foundation in \textbf{Data Structures \& Algorithms}, Machine Learning, Deep Learning, Agentic AI, Power BI, and Vector Databases.}
\end{itemize}

\end{document}
