%% Tailored CV for JioStar - ML Engineer I
%% Compiled with: lualatex main_jiostar.tex

\documentclass[11pt,a4paper,sans]{moderncv}
\moderncvstyle{banking}
\moderncvcolor{blue}

\renewcommand*{\firstnamestyle}[1]{{\fontsize{34}{36}\bfseries\upshape\color{color1}#1}}
\renewcommand*{\lastnamestyle}[1]{{\fontsize{34}{36}\bfseries\upshape\color{color1}#1}}
\renewcommand*{\sectionstyle}[1]{{\sectionfont\color{color1}#1}}

\usepackage[utf8]{inputenc}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,
    urlcolor=blue,
    pdftitle={Harsh Sachan - JioStar ML Engineer I CV},
    pdfpagemode=FullScreen,
}
\usepackage[scale=0.80]{geometry}
\usepackage{import}

\name{Harsh}{Sachan}
\address{Greater Noida, Uttar Pradesh, India}{}{}
\phone[mobile]{+91 8604304079}
\email{hsachan295@gmail.com}
\extrainfo{\href{https://linkedin.com/in/harsh-sachan-b3b24a2a2}{LinkedIn} | \href{https://github.com/hsachan295-source}{GitHub} | \href{https://leetcode.com/Harshsachan2001/}{LeetCode}}

\begin{document}

\makecvtitle

\vspace{6pt}
\small{Aspiring Machine Learning Engineer with a B.Tech in CSE (AI Specialization) from Galgotias College. Experienced in building and deploying NLP models, deep learning networks, and agentic search pipelines (RAG). Highly skilled in Python, SQL, and serving models via FastAPI/Flask, containerized with Docker for production readiness.}

\section{Core Competencies}
\vspace{1pt}
\begin{itemize}
\item \textbf{GenAI \& Natural Language Processing}: RAG, Agentic AI, LangChain, LangGraph, Sequence Classifiers, GRU, Word Embeddings, Semantic Search
\item \textbf{Machine Learning \& Deep Learning}: TensorFlow, Keras, Scikit-Learn, ANN, CNN, LSTM, Supervised/Unsupervised Learning
\item \textbf{Languages \& Databases}: Python, SQL, C++, Java, PostgreSQL, MySQL, MongoDB, Pinecone, ChromaDB
\item \textbf{Frameworks \& BI}: FastAPI, Flask, Streamlit, Pandas, NumPy, Plotly, Power BI
\item \textbf{Cloud \& Deployment}: Docker, Hugging Face Spaces, Git, GitHub, OCI, GCP
\end{itemize}

\section{Projects \& Experience}
\vspace{3pt}
\begin{itemize}

\item{\cventry{2024}{NeuralClass -- NLP Spam Classifier}{Independent}{Greater Noida, India}{}{\vspace{1pt}
\begin{itemize}
    \item Built a GRU-based sequence model for spam/ham classification with confidence scoring and logging.
    \item Served model via FastAPI REST API, containerized with Docker, and deployed on Hugging Face Spaces.
\end{itemize}}}

\vspace{3pt}

\item{\cventry{2025}{Agentic RAG System with Gemini and Pinecone}{Independent}{Greater Noida, India}{}{\vspace{1pt}
\begin{itemize}
    \item Built a Retrieval-Augmented Generation pipeline using Pinecone vector store for semantic similarity search.
    \item Implemented agentic knowledge retrieval workflows using LangChain and Gemini API for PDF question-answering.
\end{itemize}}}

\vspace{3pt}

\item{\cventry{2024}{NeuralPrice -- AI Laptop Price Predictor}{Independent}{Greater Noida, India}{}{\vspace{1pt}
\begin{itemize}
    \item Engineered a 4-layer ANN with 337 features via one-hot encoding; containerized with Docker and deployed on Hugging Face.
\end{itemize}}}

\end{itemize}

\section{Education}
\vspace{1pt}
\begin{itemize}
\item{\cventry{2022--2026}{B.Tech in Computer Science Engineering (AI Specialization)}{Galgotias College of Engineering and Technology}{Greater Noida, UP, India}{}{\vspace{1pt}
CGPA: 8.12 / 10.0\\
Key Topics: Machine Learning, Deep Learning, Natural Language Processing, Computer Vision, Generative AI.
}}
\end{itemize}

\section{Languages}
\vspace{1pt}
\begin{itemize}
\item English (Professional), Hindi (Native).
\end{itemize}

\section{Certifications}
\vspace{1pt}
\begin{itemize}
\item \textbf{Oracle}: OCI 2025 Certified Data Science Professional | OCI 2025 Certified AI Foundations Associate
\item \textbf{HackerRank}: SQL (Advanced), Problem Solving, Software Engineer Intern
\item \textbf{Google Cloud \& Experiences}: GenAI Introduction | TATA, Deloitte, Walmart Virtual Experience Certifications
\end{itemize}

\section{References}
\vspace{1pt}
\begin{itemize}
\item Available upon request.
\end{itemize}

\end{document}
