%% Tailored CV for Luxoft - Data Analyst
%% Compiled with: lualatex main_luxoft.tex

\documentclass[11pt,a4paper,sans]{moderncv}
\moderncvstyle{banking}
\moderncvcolor{blue}

\renewcommand*{\firstnamestyle}[1]{{\fontsize{34}{36}\bfseries\upshape\color{color1}#1}}
\renewcommand*{\lastnamestyle}[1]{{\fontsize{34}{36}\bfseries\upshape\color{color1}#1}}
\renewcommand*{\sectionstyle}[1]{{\sectionfont\color{color1}#1}}

\usepackage[utf8]{inputenc}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,
    urlcolor=blue,
    pdftitle={Harsh Sachan - Data Analyst CV},
    pdfpagemode=FullScreen,
}
\usepackage[scale=0.80]{geometry}
\usepackage{import}

% personal data
\name{Harsh}{Sachan}
\address{Greater Noida, Uttar Pradesh, India}{}{}
\phone[mobile]{+91 8604304079}
\email{hsachan295@gmail.com}
\extrainfo{\href{https://linkedin.com/in/harsh-sachan-b3b24a2a2}{LinkedIn} | \href{https://github.com/hsachan295-source}{GitHub} | \href{https://leetcode.com/Harshsachan2001/}{LeetCode}}

\begin{document}

\makecvtitle

\vspace{6pt}
\small{Data Analyst and Data Scientist with a B.Tech in CSE (AI Specialization) and strong analytical background. Skilled in data modeling, dashboard engineering (Power BI, Streamlit), and database optimization (PostgreSQL, MySQL). Experienced in consolidating complex enterprise data, architecting star-schema models, and driving evidence-based recommendations to improve service reliability and operational decision-making.}

% ==========================================
%     CORE COMPETENCIES
% ==========================================

\section{Core Competencies}
\vspace{1pt}
\begin{itemize}

\item \textbf{Data Analytics \& BI}: Business Intelligence, Exploratory Data Analysis (EDA), Feature Engineering, Data Visualization, Power BI dashboard design, Star Schemas, DAX, Excel

\item \textbf{Languages \& Databases}: Python, SQL, C++, Java, PostgreSQL, MySQL, MongoDB, Pinecone, ChromaDB

\item \textbf{Frameworks \& Web}: FastAPI, Flask, Streamlit, Scikit-Learn, Pandas, NumPy, Matplotlib, Seaborn, Plotly

\item \textbf{Machine Learning \& Deep Learning}: TensorFlow, Keras, ANN, CNN, GRU, LSTM, Supervised/Unsupervised Learning

\item \textbf{Tools \& Cloud}: Git, GitHub, Docker, Hugging Face Spaces, GCP, OCI

\end{itemize}

% ==========================================
%     PROJECTS / PROFESSIONAL EXPERIENCE
% ==========================================

\section{Projects \& Experience}
\vspace{3pt}
\begin{itemize}

% --- Project 1 (Analytics / BI) ---
\item{\cventry{2025}{AI \& ML Jobs Market Analytics Dashboard}{Independent}{Greater Noida, India}{}{\vspace{1pt}
\begin{itemize}
    \item Designed an executive-level Power BI dashboard analyzing global AI/ML hiring trends, salary distributions, and remote job demand.
    \item Architected star-schema data models with advanced DAX measures and calculated columns.
    \item Delivered actionable business intelligence insights for data-driven workforce and recruitment decisions.
\end{itemize}}}

\vspace{3pt}

% --- Project 2 (Data Pipelines) ---
\item{\cventry{2025}{XGBoost Student Score Predictor}{Independent}{Greater Noida, India}{}{\vspace{1pt}
\begin{itemize}
    \item Production-ready ML web app predicting exam scores from 7 academic and lifestyle features using a tuned XGBoost Regressor.
    \item Built modular Streamlit architecture with Plotly feature importance charts, deployed on Streamlit Cloud.
\end{itemize}}}

\vspace{3pt}

% --- Project 3 (Data Quality) ---
\item{\cventry{2025}{Delivery Time Predictor}{Independent}{Greater Noida, India}{}{\vspace{1pt}
\begin{itemize}
    \item Estimated delivery time predictor using a Random Forest Regressor model (100 Trees, Max Depth 10) with SLA classification (Express/Same-day/Standard).
    \item Integrated dynamic metrics and interactive sliders into a Streamlit interface.
\end{itemize}}}

\end{itemize}

% ==========================================
%     EDUCATION
% ==========================================

\section{Education}
\vspace{1pt}
\begin{itemize}

\item{\cventry{2022--2026}{B.Tech in Computer Science Engineering (AI Specialization)}{Galgotias College of Engineering and Technology}{Greater Noida, UP, India}{}{\vspace{1pt}
Cumulative Grade Point Average (CGPA): 8.12 / 10.0\\
Key Topics: Machine Learning, Deep Learning, Natural Language Processing, Computer Vision, Generative AI \& Agents, Database Management (SQL, NoSQL, Vector DBs).
}}

\end{itemize}

% ==========================================
%     LANGUAGES
% ==========================================

\section{Languages}
\vspace{1pt}
\begin{itemize}
\item English (Professional), Hindi (Native).
\end{itemize}

% ==========================================
%     CERTIFICATIONS
% ==========================================

\section{Certifications}
\vspace{1pt}
\begin{itemize}
\item \textbf{Oracle}: OCI 2025 Certified Data Science Professional | OCI 2025 Certified AI Foundations Associate
\item \textbf{IBM}: IBM SkillsBuild: Introduction to Artificial Intelligence
\item \textbf{HackerRank}: SQL (Advanced), Problem Solving, Software Engineer Intern
\item \textbf{Google Cloud \& Experiences}: Introduction to Generative AI | TATA GenAI Data Analytics | Deloitte Data Analytics
\end{itemize}

% ==========================================
%     REFERENCES
% ==========================================

\section{References}
\vspace{1pt}
\begin{itemize}
\item Available upon request.
\end{itemize}

\end{document}
