%% Tailored CV for Cubist - ML Engineer
%% Compiled with: lualatex main_cubist.tex

\documentclass[11pt,a4paper,sans]{moderncv}
\moderncvstyle{banking}
\moderncvcolor{blue}

\renewcommand*{\firstnamestyle}[1]{{\fontsize{34}{36}\bfseries\upshape\color{color1}#1}}
\renewcommand*{\lastnamestyle}[1]{{\fontsize{34}{36}\bfseries\upshape\color{color1}#1}}
\renewcommand*{\sectionstyle}[1]{{\sectionfont\color{color1}#1}}

\usepackage[utf8]{inputenc}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,
    urlcolor=blue,
    pdftitle={Harsh Sachan - Cubist ML Engineer CV},
    pdfpagemode=FullScreen,
}
\usepackage[scale=0.80]{geometry}
\usepackage{import}

\name{Harsh}{Sachan}
\address{Greater Noida, Uttar Pradesh, India}{}{}
\phone[mobile]{+91 8604304079}
\email{hsachan295@gmail.com}
\extrainfo{\href{https://linkedin.com/in/harsh-sachan-b3b24a2a2}{LinkedIn} | \href{https://github.com/hsachan295-source}{GitHub} | \href{https://leetcode.com/Harshsachan2001/}{LeetCode}}

\begin{document}

\makecvtitle

\vspace{6pt}
\small{Aspiring Machine Learning Engineer with a B.Tech in CSE (AI Specialization) from Galgotias College. Expert in building Retrieval-Augmented Generation (RAG) agents, semantic similarity search architectures, and LLM orchestration workflows. Strong foundation in Python, SQL, and deploying containerized deep learning networks.}

\section{Core Competencies}
\vspace{1pt}
\begin{itemize}
\item \textbf{Generative AI \& Agents}: RAG pipelines, Agentic AI, ReAct Agents, Tool Calling, LangGraph Workflows, LangChain, OpenAI API, Gemini API, Prompt Engineering, Semantic Search, Embeddings
\item \textbf{Languages \& Databases}: Python, SQL, C++, Java, PostgreSQL, MySQL, MongoDB, Pinecone, ChromaDB (Vector DBs)
\item \textbf{Machine Learning \& Deep Learning}: TensorFlow, Keras, Scikit-Learn, ANN, CNN, GRU, LSTM, Sequence Modeling
\item \textbf{Frameworks \& Cloud}: FastAPI, Flask, Streamlit, Docker, Hugging Face, GCP, OCI
\end{itemize}

\section{Projects \& Experience}
\vspace{3pt}
\begin{itemize}

\item{\cventry{2025}{Agentic RAG System with Gemini and Pinecone}{Independent}{Greater Noida, India}{}{\vspace{1pt}
\begin{itemize}
    \item Built a Retrieval-Augmented Generation pipeline with Pinecone vector store for semantic similarity search.
    \item Enabled PDF question answering and context-aware summarization over large document corpora.
    \item Implemented agentic knowledge retrieval workflows using LangChain and Gemini API.
\end{itemize}}}

\vspace{3pt}

\item{\cventry{2024}{NeuralClass -- NLP Spam Classifier}{Independent}{Greater Noida, India}{}{\vspace{1pt}
\begin{itemize}
    \item Built a GRU-based sequence model for spam/ham classification with confidence scoring and logging.
    \item Served model via FastAPI REST API with Docker containerization and Hugging Face deployment.
\end{itemize}}}

\vspace{3pt}

\item{\cventry{2025}{NexCart -- Full-Stack E-Commerce Product Management}{Independent}{Greater Noida, India}{}{\vspace{1pt}
\begin{itemize}
    \item FastAPI and Streamlit system; implemented Pydantic v2 cross-field validators ensuring database constraints.
\end{itemize}}}

\end{itemize}

\section{Education}
\vspace{1pt}
\begin{itemize}
\item{\cventry{2022--2026}{B.Tech in Computer Science Engineering (AI Specialization)}{Galgotias College of Engineering and Technology}{Greater Noida, UP, India}{}{\vspace{1pt}
CGPA: 8.12 / 10.0\\
Key Topics: Generative AI \& Agents, Natural Language Processing, Vector Databases, Deep Learning, SQL.
}}
\end{itemize}

\section{Languages}
\vspace{1pt}
\begin{itemize}
\item English (Professional), Hindi (Native).
\end{itemize}

\section{Certifications}
\vspace{1pt}
\begin{itemize}
\item \textbf{Oracle}: OCI 2025 Certified Data Science Professional | OCI 2025 Certified AI Foundations Associate
\item \textbf{HackerRank}: SQL (Advanced), Problem Solving, Software Engineer Intern
\item \textbf{Experiences}: Google Cloud GenAI | TATA, Deloitte, Walmart Virtual Experience Certifications
\end{itemize}

\section{References}
\vspace{1pt}
\begin{itemize}
\item Available upon request.
\end{itemize}

\end{document}
